TODO: A Survey of StarCraft AI Techniques

### 2011-09-20 survey.tex
biography test

%\begin{thebibliography}{1}
%\end{thebibliography}

\bibliographystyle{IEEEtran}                                                    
\bibliography{survey}

% biography section
% 
% If you have an EPS/PDF photo (graphicx package needed) extra braces are
% needed around the contents of the optional argument to biography to prevent
% the LaTeX parser from getting confused when it sees the complicated
% \includegraphics command within an optional argument. (You could create
% your own custom macro containing the \includegraphics command to make things
% simpler here.)
%\begin{biography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
% or if you just want to reserve a space for a photo:

\begin{IEEEbiographynophoto}{FirstName LastName}
Biography text here.
\end{IEEEbiographynophoto}

\begin{IEEEbiography}[{\includegraphics[width=2cm, keepaspectratio]{jim.jpg}}]{Jim Raynor}
Biography text here.
\end{IEEEbiography}

% if you will not have a photo at all:

% insert where needed to balance the two columns on the last page with
% biographies
%\newpage

% You can push biographies down or up by placing
% a \vfill before or after them. The appropriate
% use of \vfill depends on what kind of text is
% on the last page and whether or not the columns
% are being equalized.

%\vfill

% Can be used to pull up biographies so that the bottom of the last one
% is flush with the other column.
%\enlargethispage{-5in}

% that's all folks
\end{document}

>>>>

%\begin{thebibliography}{1}
%\end{thebibliography}
\bibliographystyle{IEEEtran}                                                    
\bibliography{survey}

%\begin{IEEEbiographynophoto}{FirstName LastName}
%Biography text here.
%\end{IEEEbiographynophoto}

\begin{IEEEbiography}[{\includegraphics[width=2cm, keepaspectratio]{jim.jpg}}]{Jim Raynor}
Jim Raynor was a Confederate marshal on Mar Sara at the time of the first zerg incursions on that world. He is now with Raynor's Raiders Inc.
\end{IEEEbiography}

\end{document}
